Comparing probabilistic predictive models applied to football

### 2015-08-20 template.tex
tentativa de responder ao famigerado ponto 2

@@

@@

	We therefore conclude that all methods have similar predictive power, and none of them is more informative in average.
	Nevertheless, all methods yielded better predictions than the trivial prediction, and they are well-calibrated.

@@

{\color{blue}The fact that simple models are often as effective as their competitors is often unnoticed by users of such methods, which leads to the overuse of models that are often
	hard to interpret and to implement, and that also require one to keep track of several covariates. We would call this phenomenon the {\it king's nudity}  in allusion to Anderson's {\it The Emperor's New Clothes}, \cite{emperor}: ``But he isn't wearing anything at all!''. In this spirit, since we have explored only the prediction of football matches in the specific case o Brazilian football championship, we would like to study if the same extends to other fields such as, for instance, weather or economics forecasts.}

		If, on the one hand, our findings appear as another supportive example of Ockham's razor, on the other they pose several questions about probabilistic prediction of sport events.
		In particular, based on the fact that the models have similar performance, one may ask: is there an irreducible ``randomness'' or ``degree of unpredictability'' implicit in these events?
		Is this degree an indicator of how tight or leveled is the championship being studied?

>>>>

\definecolor{darkgreen}{RGB}{15,127,0}

@@

	{\color{darkgreen}Our analyses therefore show that, marginally, all methods yield similar scores in average, i.e., they have similar predictive power. A related question
	is whether, at each match, the performance of the methods is also similar. Figure \ref{fig::scores2} displays pairwise comparisons
	of the various score between the five models we investigate. All methods present
	a reasonable agreement among each other. Evidently, the Multinomial-Dirichlet models
	are the ones where there is largest agreement. To formally test the hypotheses that the models yield the same scores in average for
	each match,
	we use Friedman's rank sum test. All p-values are not significant at the level 5\% (Brier: 0.077; Spherical: 0.055; Proportion
	of errors: 0.655), except for the logarithmic
	score, which has p-value of 0.021. Post-hoc analyses show that the differences are in Mn-Dir$_1$ versus BB2 (p=0.031),
	Mn-Dir$_2$ versus BB1 (p=0.043), and Mn-Dir$_3$ versus BB1 (p=0.030). These results thus indicate that BB1 and BB2
	are similar to each other in terms of predictive power, while the performance of Mn-Dir models differ from the BB's \emph{for each match}.
	We therefore conclude that while the models we investigate may yield different scores for each
	match according to some metrics, the overall scores are similar. That is, while in some matches Mn-Dir models
	have better results, for others BB models have better performance. However, in the long term, all methods have similar accuracy.
	}

		\begin{figure}[H]
			\centering
			\includegraphics[page=13,scale=0.48]{futebolComparacaoModelosForPaper.pdf}
			\includegraphics[page=14,scale=0.48]{futebolComparacaoModelosForPaper.pdf}\\
			\caption{Pairwise comparison of the various scores. Left plot: upper right plots display Brier Scores;
			lower left plots display Logarithmic Scores. Right plot: upper right plots display proportion of agreements
			between methods; lower left  plots display Spherical Scores. Red line represents the identity $x=y$.}
			\label{fig::scores2}
		\end{figure}

@@

	{\color{darkgreen}We therefore conclude that 
	although the accuracy of each method may depend on the specific characteristics of each match,
	all methods have similar predictive power, and none of them is more informative  in average. 
    Moreover, all methods yielded better predictions than the trivial prediction, and they were all well-calibrated.}

@@

{\color{blue}The fact that simple models are often as effective as their competitors in average is often unnoticed by users of such methods, which leads to the overuse of models that are often
	hard to interpret and to implement, and that also require one to keep track of several covariates. We would call this phenomenon the {\it king's nudity}  in allusion to Anderson's {\it The Emperor's New Clothes}, \cite{emperor}: ``But he isn't wearing anything at all!''. In this spirit, since we have explored only the prediction of football matches in the specific case o Brazilian football championship, we would like to study if the same extends to other fields such as, for instance, weather or economics forecasts.}

		If, on the one hand, our findings appear as another supportive example of Ockham's razor, on the other they pose several questions about probabilistic prediction of sport events.
		In particular, based on the fact that the models have similar {\color{darkgreen}predictive power in average}, one may ask: is there an irreducible ``randomness'' or ``degree of unpredictability'' implicit in these events?
		Is this degree an indicator of how tight or leveled is the championship being studied?
